Millions of Type Errors

### 2023-05-10 oopsla23/paper.tex
example timelines

>>>>

TODO nocheck accumulated errors?

\subsection{Example Sessions}

FILL example sessions.

\Cref{f:ex-session-strict} begins in strict mode
but jumps to nocheck mode as well.
The jumps sometimes coincide with module switches (vertical line),
sometimes not.
The green line counts type errors.in the codebase.

\begin{figure}[t]
  \includegraphics[width=0.7\columnwidth]{img/example-session-strict.pdf}
  \caption{Example strict session}
  \label{f:ex-session-strict}
\end{figure}

\Cref{f:ex-session-nonstrict} presents the three sessions from \mnonstrict{} mode
that have the greatest number of events (not necessarily the longest time spans).
There are no module or mode switches.
There are few type errors.
One high point shows 10 errors, but these errors are gone (probably fixed) at
the next event.

\begin{figure}[t]
  \includegraphics[width=0.7\columnwidth]{img/example-session-nonstrict.pdf}
  \caption{Three most populated nonstrict sessions}
  \label{f:ex-session-nonstrict}
\end{figure}

\Cref{f:ex-session-nocheck} shows a roller coaster from \mnocheck{} mode.
Several hundred ForcedStrict type errors appear and disappear between events.
There are lots of module switches too \ldots but that makes no difference
for these project-wide error counts.

\begin{figure}[t]
  \includegraphics[width=0.7\columnwidth]{img/example-session-nocheck.pdf}
  \caption{Example nocheck session}
  \label{f:ex-session-nocheck}
\end{figure}

\subsection{Aggregate Sessions}
